---
title: "Supplementing the Rosés-Wolf database on regional GDP"
format: html
execute: 
  echo: false
  message: false
  warning: false
---

## Purpose

We want to supplement the database on regional GDP that we are going to provide to students.

I have collected a range of data at the NUTS2 level (though it is only for the year 2015).

They are shown in the table below, where the header is coloured blue for the category:

```{r}
library(tidyverse)
library(sf)
library(gt)

df <- read_rds(here::here("data/regions_illustrated.rds")) %>% 
  rename(nuts_code = code)
  
map <- read_rds(here::here("data/map_simple.rds"))
```

```{r}
df_map <- df %>% 
  inner_join(map)
```

```{r}
# indicators <- df_map %>% 
#   group_by(stat_domain) %>% 
#   count(indicator) %>% 
#   select(-n) %>% 
#   ungroup()
# 
# tab_indicators <- function(stat_domain_id) {
#   indicators %>%
#     filter(stat_domain == stat_domain_id) %>%
#     distinct(indicator) %>%
#     gt() %>%
#     tab_header(title = md(glue::glue("**{stat_domain_id}**"))) %>%
#     tab_options(column_labels.hidden = T)
# }
# 
# for (i in unique(indicators$stat_domain)) {
#   tab_indicators(i)
# }

df_map %>%
  group_by(stat_domain) %>%
  count(indicator) %>%
  select(-n) %>%
  gt() %>%
  tab_style(
    style = list(
      cell_fill(color = "#191970"),
      cell_text(color = "white")
    ),
    locations = cells_row_groups(groups = everything())
  ) %>%
  tab_header(title = md("**List of indicators**")) %>%
  tab_options(column_labels.hidden = T)
```

We can draw plots list this with the data: showing the relationship between economic activity and gdp

```{r}

df_map %>%
  filter(indicator %in% c(
    "Economic activity rate (% of population aged 15-64)",
    "Gross domestic product (Euro per inhabitant)"
  )) %>%
  select(-stat_domain) %>%
  distinct() %>%
  pivot_wider(names_from = indicator, values_from = value) %>%
  mutate(country = fct_lump(country, 8)) %>%
  ggplot(aes(`Gross domestic product (Euro per inhabitant)`, `Economic activity rate (% of population aged 15-64)`, colour = country)) +
  geom_point() +
  labs(colour = "Country")
```

We can also make a map of the Economic Activity Rate:

```{r}
df_map %>%
  filter(indicator %in% c(
    "Economic activity rate (% of population aged 15-64)",
    "Gross domestic product (Euro per inhabitant)"
  )) %>%
  select(-stat_domain) %>%
  distinct() %>%
  pivot_wider(names_from = indicator, values_from = value) %>%
  ggplot(aes(fill = `Economic activity rate (% of population aged 15-64)`, geometry = geometry)) +
  geom_sf() +
  coord_sf() +
  scale_fill_viridis_c(labels = scales::percent_format()) +
  labs(fill = "Economic activity rate\n(% of population aged 15-64)")

```

This is the relationship between GDP and medical doctors per 100 000 inhabitants.

```{r}
df_map %>%
  filter(indicator %in% c(
    "Medical doctors (per 100 000 inhabitants)",
    "Gross domestic product (Euro per inhabitant)"
  )) %>%
  select(-stat_domain) %>%
  distinct() %>%
  pivot_wider(names_from = indicator, values_from = value) %>%
  mutate(country = fct_lump(country, 8)) %>%
  ggplot(aes(`Gross domestic product (Euro per inhabitant)`, `Medical doctors (per 100 000 inhabitants)`, colour = country)) +
  geom_point() +
  geom_smooth(aes(group = 1)) +
  labs(colour = "Country")
```

